---
title: "NXP Datasheet Commonality"
output: html_notebook
---

To run it, use the following as a template. Before running do the following.
Go into the CSV and perform the following:
1. Add a label the first cell (matrix[0][0]) to 'category_1'
2. Change the names of the titles if it is too long

```{r, warning = FALSE, message = FALSE}
library(tidyverse)
library(RColorBrewer)
library(gcookbook)
```

MAJOR CATEGORIES
Figure 1: Cross-Sector of Sharing Semiconductor Chips (Datasheets and Datasheet Families), Example - NXP Microprocessors and Microcontrol Units
```{r, warning = FALSE, message = FALSE}
# load dataset
data <- read.csv('major_categories.csv')

data <- data %>% 
  select(-c("Automotive")) %>% # change this to the column populated of 0's if exists
  pivot_longer(cols = -c(category_1), names_to = "category_2",  values_to = "overlap") %>% 
  mutate(overlap = case_when(
    overlap == 0 ~ NA_integer_, 
    TRUE ~ overlap
  )) 

mypal <- c(brewer.pal(9, "YlOrRd"), brewer.pal(9, "YlOrBr")[9])

data %>% 
  group_by(category_2) %>%
  mutate(max_overlap = max(overlap)) %>%
  ggplot(aes(reorder(category_1, max_overlap), category_2, fill = as.factor(overlap), label = overlap)) + 
  geom_point(shape = 21, aes(size=overlap)) + 
  geom_text(vjust=-2) + 
  guides(fill = FALSE, size = FALSE) + 
  labs(x = "", y = "") + 
  theme_minimal() + 
  scale_fill_manual(values = mypal)  +
  scale_x_discrete(position = "top") + 
  ggtitle("Figure 1: Cross-Sector of Sharing Semiconductor Chips 
          (Datasheets and Datasheet Families) 
          Example from NXP Microprocessors and Microcontrol Units") + 
  theme(plot.title = element_text(hjust = 0.5))
```
FIGURE 2: Largest Sharing of Semiconductor Chips Across Sector Subcategories: Example - NXP Microprocessors and MCUs
```{r, warning = FALSE, message = FALSE}
data <- read.csv('largest_subcategories_diff_group.csv')
plot <- ggplot(data, aes(x = Category_Pair_Name, y = Count)) +
  geom_col() +
  geom_text(aes(label = Count), hjust= 2, vjust = 0.5, colour = "white") +
  ggtitle("Figure 2: Top 10 Largest Sharing of 
  Semiconductor Chips Across 
  Sector Subcategories:
          \n Example: 
  NXP Microprocessors and MCUs") + 
  theme(plot.title = element_text(hjust = 0.5))

plot + coord_flip() + labs(x = "Subcategory Pairs", y = "Datasheet Counts") #makes it horizontal
```
AUTOMOTIVE CATEGORIES
FIGURE 3: Shared Semiconductor Chips (Datasheets and Datasheet families) within Automotive Applications: Example - NXP Microprocessors and MCUs
```{r, warning = FALSE, message = FALSE}
# load dataset
data <- read.csv('automotive_commonality.csv')

data <- data %>% 
  select(-c("AutomatedDriving")) %>% # change this to the column populated of 0's if exists
  pivot_longer(cols = -c(category_1), names_to = "category_2",  values_to = "overlap") %>% 
  mutate(overlap = case_when(
    overlap == 0 ~ NA_integer_, 
    TRUE ~ overlap
  )) 

mypal <- c(brewer.pal(9, "YlOrRd"), brewer.pal(9, "YlOrBr")[9])

data %>% 
  group_by(category_2) %>% 
  mutate(max_overlap = max(overlap)) %>%
  ggplot(aes(reorder(category_1, max_overlap), category_2, fill = as.factor(overlap), label = overlap)) + 
  geom_point(shape = 21, aes(size=overlap)) + 
  geom_text(vjust=-2) + 
  guides(fill = FALSE, size = FALSE) + 
  labs(x = "", y = "") + 
  theme_minimal() + 
  scale_fill_manual(values = mypal)  +
  scale_x_discrete(position = "top") + 
  ggtitle("Figure 3: Shared Semiconductor Chips within Automotive Applications
          \n (Datasheets and Datasheet families) 
          \n Example - NXP Microprocessors and MCUs") + 
  theme(plot.title = element_text(hjust = 0.5))
```

INDUSTRIAL CATEGORIES
FIGURE 4:  Shared Semiconductor Chips (Datasheets and Datasheet families) within Industrial Applications: Example - NXP Microprocessors and MCUs
```{r, warning = FALSE, message = FALSE}
# load dataset
data <- read.csv('Industrial_commonality.csv')

data <- data %>% 
  select(-c("Robotics")) %>% # change this to the column populated of 0's if exists
  pivot_longer(cols = -c(category_1), names_to = "category_2",  values_to = "overlap") %>% 
  mutate(overlap = case_when(
    overlap == 0 ~ NA_integer_, 
    TRUE ~ overlap
  )) 

mypal <- c(brewer.pal(9, "YlOrRd"), brewer.pal(9, "YlOrBr")[9])

data %>% 
  group_by(category_2) %>%
  mutate(max_overlap = max(overlap)) %>%
  ggplot(aes(reorder(category_1, max_overlap), category_2, fill = as.factor(overlap), label = overlap)) + 
  geom_point(shape = 21, aes(size=overlap)) + 
  geom_text(vjust=-2) + 
  guides(fill = FALSE, size = FALSE) + 
  labs(x = "", y = "") + 
  theme_minimal() + 
  scale_fill_manual(values = mypal)  +
  scale_x_discrete(position = "top") + 
  ggtitle("Figure 4: Shared Semiconductor Chips within Industrial Applications
          \n (Datasheets and Datasheet families) 
          \n Example - NXP Microprocessors and MCUs") + 
  theme(plot.title = element_text(hjust = 0.5))  
```